Autoignition of Methyl Valerate at Low to Intermediate Temperatures and Elevated Pressures in a Rapid Compression Machine

### 2017-06-27 methyl-valerate.tex
Add updates to paper
Update vapor pressure

\documentclass[letterpaper,review]{elsarticle}

@@

\begin{figure}
    \centering
    \resizebox{\linewidth}{!}{\input{figures/ignition_delay_definition.pgf}}
    \caption{Definition of the ignition delays used in this work. The
    experiment in this figure was conducted for a \(\phi=2.0\) mixture with
    \mbox{\(\ce{Ar}/(\ce{N2}+\ce{AR})=0.5\)}, \(P_0=\SI{0.7694}{\bar}\),
    \(T_0=\SI{373}{\K}\), \(P_C=\SI{14.94}{\bar}\), \(T_C=\SI{723}{\K}\),
    \(\tau=\SI{27.44\pm0.99}{\ms}\), \(\tau_1=\SI{16.57\pm0.48}{\ms}\).}
    \label{fig:ign-delay-def}
\end{figure}

@@

\begin{table}
    \centering
    \caption{Mixtures considered in this work}
    \begin{tabular}{Sccccc}
        \toprule
        {\(\phi\)} & \multicolumn{4}{c}{Mole Fraction (purity)} & \ce{Ar}/(\ce{N2} + \ce{Ar}) \\
        \cmidrule{2-5}
         & \ce{MV} (\SI{100}{\percent}) & \ce{O2} (\SI{99.994}{\percent}) & \ce{Ar} (\SI{99.999}{\percent}) & \ce{N2} (\SI{99.999}{\percent}) &  \\
        \midrule
        0.25 & 0.0065 & 0.2087 & 0.7848 & 0.0000 & 1.0 \\
        0.5 & 0.0130 & 0.2074 & 0.7798 & 0.0000 & 1.0 \\
        1.0 & 0.0256 & 0.2047 & 0.7697 & 0.0000 & 1.0 \\
        1.0 & 0.0256 & 0.2047 & 0.3849 & 0.3848 & 0.5 \\
        2.0 & 0.0499 & 0.1996 & 0.0000 & 0.7505 & 0.0 \\
        2.0 & 0.0499 & 0.1996 & 0.3752 & 0.3753 & 0.5 \\
        \bottomrule
    \end{tabular}
    \label{tab:mixtures}
\end{table}

@@

The initial temperature is chosen such that the saturated vapor pressure \((P_{\text{sat}})\) of the
fuel at the initial temperature is at least twice the partial pressure of the fuel in the mixing
tank. The Antoine equation
%
\begin{equation}\label{eq:antoine}
    \logten{P_{\text{sat}}} = A - \frac{B}{T - C}
\end{equation}
%
is used to model the saturated vapor pressure of MV as a function of temperature, where \(A\),
\(B\), and \(C\) are substance-specific coefficients. Coefficients for \cref{eq:antoine} are given
in the literature by~\citet{Ortega2003}, \citet{Camacho2007}, and \citet{Stephenson1987};
unfortunately, the values of the coefficients are different among all three authors. Therefore,
coefficients for use in \cref{eq:antoine} are determined in this work by least squares fitting of
the data of \citet{Ortega2003}, \citet{vanGenderen2002}, and \citet{Verevkin2008} using the
\verb|curve_fit()| function of SciPy~\cite{Jones2001} version 0.19.0. \Cref{fig:vapor-pressure}
shows that the coefficients fit with this procedure give good agreement with the experimental data;
values for the coefficients computed in this work and in the literature works are given in
\cref{tab:antoine}. The data used to calculate the coefficients are provided in the Supplementary
Material.

\begin{figure}
    \centering
    \resizebox{\linewidth}{!}{\input{figures/vapor_pressure.pgf}}
    \caption{Saturated vapor pressure of MV as a function of temperature,
    plotted using the Antoine equation, \cref{eq:antoine}, with
    \(A=6.4030\), \(B=1528.69\), and \(C=52.881\).}
    \label{fig:vapor-pressure}
\end{figure}

\begin{table}
    \centering
    \caption{Antoine Equation coefficients computed in this work and from the
    literature. The $2\sigma$ confidence interval is estimated by taking the
    square root of the diagonals of the covariance matrix returned from
    \texttt{curve\_fit()}}
    \label{tab:antoine}
    \begin{tabular}{cccccc}
        \toprule
        & $A$ & $B$ & $C$ & $T_{\text{min}}$, \si{\K} & $T_{\text{max}}$, \si{\K} \\
        \midrule
        This Work & 6.4030 & 1528.69 & 52.881 & 274.9 & 417.18 \\
        $2\sigma$ Confidence Interval & 0.0919 & 53.47 & 4.934 & --- & --- \\
        \cite{Ortega2003} & 6.23175 & 1429.00 & 62.30 & 364.75 & 417.18 \\
        \cite{Camacho2007} & 5.9644 & 1281.06 & 75.94 & 281 & 547 \\
        \cite{Stephenson1987} & 6.62646 & 1658.4 & 42.09 & 297 & 411 \\
        \bottomrule
    \end{tabular}
\end{table}

@@

\begin{figure}[htb]
    \centering
    \input{figures/ignition-delays.pgf}
    \caption{Ignition delays of MV as a function of inverse temperature. Filled
    points are the overall ignition delays and hollow points are the first stage
    ignition delays. a) \SI{15}{\bar}. b) \SI{30}{\bar}}
    \label{fig:ignition-delays}
\end{figure}

>>>>

\documentclass[letterpaper, review]{elsarticle}

@@

\begin{center}
    \captionsetup{type=figure}
    \includegraphics{figures/ignition_delay_definition.pdf}
    \caption{Definition of the ignition delays used in this work. The
    experiment in this figure was conducted for a \(\phi=2.0\) mixture with
    \mbox{\(\ce{Ar}/(\ce{N2}+\ce{AR})=0.5\)}, \(P_0=\SI{0.7806}{\bar}\),
    \(T_0=\SI{373}{\K}\), \(P_C=\SI{14.92}{\bar}\), \(T_C=\SI{720}{\K}\),
    \(\tau=\SI{27.56\pm0.89}{\ms}\), \(\tau_1=\SI{16.60\pm0.46}{\ms}\).}
    \label{fig:ign-delay-def}
\end{center}

@@

\begin{center}
    \captionsetup{type=table}
    \caption{Mixtures considered in this work}
    \begin{tabular}{Sccccc}
        \toprule
        {\(\phi\)} & \multicolumn{4}{c}{Mole Fraction (purity)} & \ce{Ar}/(\ce{N2} + \ce{Ar}) \\
        \cmidrule{2-5}
         & \ce{MV} (\SI{100}{\percent}) & \ce{O2} (\SI{99.994}{\percent}) & \ce{Ar} (\SI{99.999}{\percent}) & \ce{N2} (\SI{99.999}{\percent}) &  \\
        \midrule
        0.25 & 0.0065 & 0.2087 & 0.7848 & 0.0000 & 1.0 \\
        0.5 & 0.0130 & 0.2074 & 0.7798 & 0.0000 & 1.0 \\
        1.0 & 0.0256 & 0.2047 & 0.7697 & 0.0000 & 1.0 \\
        1.0 & 0.0256 & 0.2047 & 0.3849 & 0.3848 & 0.5 \\
        2.0 & 0.0499 & 0.1996 & 0.0000 & 0.7505 & 0.0 \\
        2.0 & 0.0499 & 0.1996 & 0.3752 & 0.3753 & 0.5 \\
        \bottomrule
    \end{tabular}
    \label{tab:mixtures}
\end{center}

@@

The initial temperature is chosen such that the saturated vapor pressure \((P_{\text{sat}})\) of the
fuel at the initial temperature is at least twice the partial pressure of the fuel in the mixing
tank. The Antoine equation
%
\begin{equation}\label{eq:antoine}
    \logten{P_{\text{sat}}} = A - \frac{B}{T - C}
\end{equation}
%
is used to model the saturated vapor pressure of MV as a function of temperature, where \(A\),
\(B\), and \(C\) are substance-specific coefficients. Coefficients for \cref{eq:antoine} are given
in the literature by~\citet{Ortega2003}, \citet{Camacho2007}, and~\citet{Stephenson1987}.
Unfortunately, the values of the coefficients are different among all three authors and, more
importantly, the temperature ranges provided in those three fits do not cover the entire range of
interest for this study. Therefore, coefficients for use in \cref{eq:antoine} are determined in this
work by least squares fitting of the data of \citet{Ortega2003}, \citet{vanGenderen2002}, and
\citet{Verevkin2008} using the \verb|curve_fit()| function of SciPy~\cite{Jones2001} version 0.19.0.
\Cref{fig:vapor-pressure} shows that the coefficients fit with this procedure give good agreement
with the experimental data; values for the coefficients computed in this work and in the literature
works are given in \cref{tab:antoine}. The data used to calculate the coefficients are provided in
the Supplementary Material.

\begin{center}
    \captionsetup{type=figure}
    \input{figures/vapor_pressure.pgf}
    \caption{Saturated vapor pressure of MV as a function of temperature,
    plotted using the Antoine equation, \cref{eq:antoine}, with
    \(A=6.4030\), \(B=1528.69\), and \(C=52.881\).}
    \label{fig:vapor-pressure}
\end{center}

\begin{center}
    \captionsetup{type=table}
    \caption{Antoine Equation coefficients computed in this work and from the
    literature. The $2\sigma$ confidence interval is estimated by taking the
    square root of the diagonals of the covariance matrix returned from
    \texttt{curve\_fit()}}
    \label{tab:antoine}
    \begin{tabular}{cccccc}
        \toprule
        & $A$ & $B$ & $C$ & $T_{\text{min}}$, \si{\K} & $T_{\text{max}}$, \si{\K} \\
        \midrule
        This Work & 6.4030 & 1528.69 & 52.881 & 274.9 & 417.18 \\
        $2\sigma$ Confidence Interval & 0.0919 & 53.47 & 4.934 & --- & --- \\
        \citet{Ortega2003} & 6.23175 & 1429.00 & 62.30 & 364.75 & 417.18 \\
        \citet{Camacho2007} & 5.9644 & 1281.06 & 75.94 & 281 & 547 \\
        \citet{Stephenson1987} & 6.62646 & 1658.4 & 42.09 & 297 & 411 \\
        \bottomrule
    \end{tabular}
\end{center}

@@

\begin{figure}[htb]
    \centering
    \resizebox{\linewidth}{!}{\input{figures/ignition-delays.pgf}}
    \caption{Ignition delays of MV as a function of inverse temperature. Filled
    points are the overall ignition delays and hollow points are the first stage
    ignition delays. a) \SI{15}{\bar}. b) \SI{30}{\bar}}
    \label{fig:ignition-delays}
\end{figure}
